plyranges: a grammar for transforming genomics data

### 2018-04-23 paper.Rmd
overlap figure now in place.

Our algebra recasts the actions of finding overlaps or nearest neighbours 
between two genomic regions as a relational join operator. The join operator 
acts on two GRanges object, a query and a subject. The join operator is 
relational in the sense that metadata from the query and subject ranges is 
retained in the joined range.  The commonality between
all join operators in the `plyranges` DSL is to use the index of where in
the query range the subject range 'hits' the query range as a primary key 
(figure *need to make figure*). The notion of 'hits' and hence
the resulting key is determined by the type of join (preceding, nearest, follows
overlaps).

We extend this idea by introducing three types of overlap joins: inner,
intersect and left. The inner join considers a hit to be any overlap between
subject and query and expands the query range to have length equal to the 
number of hits. The intersect join uses the same definition of a hit as
the inner join but returns a range where the start and end coordinates
are the intersect of coordinates in the subject that hit the query. Finally,
the overlap left join is akin to left outer join in Cobb's relational algebra:
it performs an overlap inner join but also returns all query ranges that
are not hit by the subject.

>>>>

Our algebra recasts the actions of finding overlaps or nearest neighbours 
between two genomic regions as a relational join operator. The join operator 
acts on two GRanges object, a query and a subject. The join operator is 
relational in the sense that metadata from the query and subject ranges is 
retained in the joined range.  The commonality between
all join operators in the `plyranges` DSL is to use the index of where in
the query range the subject range 'hits' the query range as a primary key 
(figure \ref{fig:olaps-fig}). The notion of 'hits' and hence
the resulting key is determined by the type of join (preceding, nearest, follows
overlaps).

```{r olaps-fig, echo = FALSE, out.width="400pt", fig.cap="Illustration of the three overlap join operators. Each join takes query and subject range as input (black and grey rectangles, respectively) with associated metadata (pink and orange rectangles respectively). An index for the join is computed via returning a Hits object, which contains the indices of where the subject overlaps the query range. This index is used to expand the query or (take the intersect) of the query ranges with subject ranges and return metadata associated with each input. This principle is gnerally applied through the `plyranges` DSL for both overlaps and nearest neighbour operations."}
knitr::include_graphics("olaps-figure.png")
```
We extend this idea by introducing three types of overlap joins: inner,
intersect and left (figure \ref{fig:olaps-fig}). The inner join considers a
hit to be any overlap between subject and query and expands the query range to 
have length equal to the  number of hits. The intersect join uses the same 
definition of a hit as the inner join but returns a range where the start and end coordinates
are the intersect of coordinates in the subject that hit the query. Finally,
the overlap left join is akin to left outer join in Cobb's relational algebra:
it performs an overlap inner join but also returns all query ranges that
are not hit by the subject.

### 2018-04-23 paper.tex
overlap figure now in place.

Several domain specific languages (DSLs) enable scientists to process
and reason about heterogeneous genomics data heterogeneous genomics data
by expressing common operations, such as range manipulation and
overlap-based joins, using the vocabulary of genomics. Their
implementations either delegate computations to a database, or operate
over collections of files in standard formats like BED.An example of the
former is the Genome Query Language (GQL) and its distributed
implementation GenAp which use an SQL-like syntax for fast retrieval of
information of unprocessed sequencing data {[}1{]}; {[}2{]}. Similarly,
the Genometric Query Language (GMQL) implements a relational algebra for
combining genomic datasets {[}3{]}. The command line application
BEDtools develops an extensive algebra for performing arithmetic between
two or more sets of genomic regions {[}4{]}. All of the aforementioned
DSLs are designed to be evaluated either at the command line or embedded
in scripts for batch processing. They exist in sparse ecosystem, mostly
consisting of UNIX and database tools that lack biological semantics and
operate at the level of files and database tables.

@@

The Bioconductor infrastructure models the genomic data and operations
from the perspective of the power user, one who understands and wants to
take advantage of the subtle differences in data types. This design has
enabled the development of sophisticated tools, as evidenced by the
hundreds of packages depending the framework. Unfortunately, the myriad
of data structures have overlapping purposes and important but obscure
differences in behaviour that often confuse the typical end user.

Recently, there has been a concerted, community effort to standardize R
data structures and workflows around the notion of tidy data {[}10{]}. A
tidy dataset is defined to be to a tabular data structure that has
observations as rows and columns as variables, and each tidy dataset
represents measurements from a single observational unit. The tidy data
pattern is useful because it allows us to see how the data relates to
the design of an experiment and the variables measured. The
\texttt{dplyr} package {[}11{]} defines an API that maps notions from
the general relational algebra to operations on tidy data. It expresses
each operation as a cohesive, endomorphic verb. Taken together these
features enable a user to write human readable analysis workflows.

@@

The \texttt{plyranges} DSL is built on the most general Bioconductor
data structure, GRanges, which is capable of representing all types of
genomic data at a semantic level that roughly matches the intuition of
most users. A GRanges is essentially a table, with columns for the
chromosome, start and end coordinates, and the strand, along with an
arbitrary set of additional columns, consisting of measurements or
metadata specific to the data type or experiment. For example a GRanges
can be used to represent a gene with its chromosomal coordinates, and
along with its exon identifiers; or a GRanges can represent an RNA-seq
experiment as a set of genes with a corresponding count column.

By definition the GRanges follow the tidy data pattern: it is a
rectangular table corresponding to a single biological context. Each row
contains a single observation and each column is a variable about that
observation. Hence, we have designed the \texttt{plyranges} DSL to
extend the grammar and design principles of \texttt{dplyr}: cohesion,
consistency, endomorphism, and fluency. All of these principles are
defined and discussed below in the context of the GRanges class. Where
applicable we contrast our design to the existing Bioconductor
infrastructure.

@@

Our algebra recasts the actions of finding overlaps or nearest
neighbours between two genomic regions as a relational join operator.
The join operator acts on two GRanges object, a query and a subject. The
join operator is relational in the sense that metadata from the query
and subject ranges is retained in the joined range. The commonality
between all join operators in the \texttt{plyranges} DSL is to use the
index of where in the query range the subject range `hits' the query
range as a primary key (figure \emph{need to make figure}). The notion
of `hits' and hence the resulting key is determined by the type of join
(preceding, nearest, follows overlaps).

more comparison to Bioconductor API here? table of join ops?

@@

@@

\subsection{Limitations}\label{limitations}

A caveat to constructing a compatible interface with \texttt{dplyr} is
that \texttt{plyranges} makes extensive use of non-standard evaluation
in R (achieved via the \texttt{rlang} package {[}14{]}). Simply, this
means that computations are performed and evaluated in the context of
the GRanges objects, which emphasises the interactive nature of the
interface. This has the disadvantage that programming with
\texttt{plyranges} becomes more difficult because a user needs to know
about non-standard evaluation and user defined functions can be
difficult to debug.

@@

Here we provide examples on how to use the \texttt{plyranges} DSL to
construct genomic data workflows.

@@

We use the Bioconductor package \emph{AnnotationHub} {[}15{]} to search
for BigWig files from ChIP-Seq experiments from the Human Epigenome
Roadmap project {[}16{]}. We choose to focus on assays for primary T
CD8+ memory cells from peripheral blood. We can then read the BigWig
file corresponding to the H3 lysine 27 trimethylation (H3K27Me3)
methylation mark over chromosome 10.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{chr10_scores <-}\StringTok{ }\NormalTok{bw_file }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{read_bigwig}\NormalTok{(}\DataTypeTok{overlap_ranges =}\NormalTok{ chr10_ranges) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{set_genome_info}\NormalTok{(}\DataTypeTok{genome =} \StringTok{"hg19"}\NormalTok{)}
\NormalTok{chr10_scores}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
#> GRanges object with 5789841 ranges and 1 metadata column:
#>             seqnames                 ranges strand |              score
#>                <Rle>              <IRanges>  <Rle> |          <numeric>
#>         [1]    chr10         [    1, 60602]      * | 0.0422799997031689
#>         [2]    chr10         [60603, 60781]      * |  0.163240000605583
#>         [3]    chr10         [60782, 60816]      * |  0.372139990329742
#>         [4]    chr10         [60817, 60995]      * |  0.163240000605583
#>         [5]    chr10         [60996, 61625]      * | 0.0422799997031689
#>         ...      ...                    ...    ... .                ...
#>   [5789837]    chr10 [135524723, 135524734]      * |  0.144319996237755
#>   [5789838]    chr10 [135524735, 135524775]      * |  0.250230014324188
#>   [5789839]    chr10 [135524776, 135524784]      * |  0.427789986133575
#>   [5789840]    chr10 [135524785, 135524806]      * |  0.730019986629486
#>   [5789841]    chr10 [135524807, 135524837]      * |   1.03103005886078
#>   -------
#>   seqinfo: 25 sequences from hg19 genome
\end{verbatim}

@@

@@

(example of group\_by\_overlaps + summarise)

\subsection{Transition Transversion
Ratio}\label{transition-transversion-ratio}

(example of group\_by + mutate + summarise and working on an object that
inherits from GRanges)

@@

The \emph{plyranges} package is available on the Bioconductor project
website \url{https://bioconductor.org} or can be accessed via Github
\url{https://github.com/sa-lee/plyranges}. We aim to continue developing
the \texttt{plyranges} package and extend it for use with more complex
data structures such as the \emph{SummarizedExperiment} class, which can
be used for analysing transcriptomic and variant data. As the
\texttt{plyranges} interface encourages tidy data practices it
integrates well with the principles of the grammar of graphics, we aim
to use it to prepare data for the visualisation of multimodal biological
datasets.

@@

>>>>

Several domain specific languages (DSLs) enable scientists to process
and reason about heterogeneous genomics data by expressing common
operations, such as range manipulation and overlap-based joins, using
the vocabulary of genomics. Their implementations either delegate
computations to a database, or operate over collections of files in
standard formats like BED. An example of the former is the Genome Query
Language (GQL) and its distributed implementation GenAp which use an
SQL-like syntax for fast retrieval of information of unprocessed
sequencing data {[}1{]}; {[}2{]}. Similarly, the Genometric Query
Language (GMQL) implements a relational algebra for combining genomic
datasets {[}3{]}. The command line application BEDtools develops an
extensive algebra for performing arithmetic between two or more sets of
genomic regions {[}4{]}. All of the aforementioned DSLs are designed to
be evaluated either at the command line or embedded in scripts for batch
processing. They exist in a sparse ecosystem, mostly consisting of UNIX
and database tools that lack biological semantics and operate at the
level of files and database tables.

@@

The Bioconductor infrastructure models the genomic data and operations
from the perspective of the power user, one who understands and wants to
take advantage of the subtle differences in data types. This design has
enabled the development of sophisticated tools, as evidenced by the
hundreds of packages depending on the framework. Unfortunately, the
myriad of data structures have overlapping purposes and important but
obscure differences in behaviour that often confuse the typical end
user.

Recently, there has been a concerted, community effort to standardize R
data structures and workflows around the notion of tidy data {[}10{]}. A
tidy dataset is defined as a tabular data structure that has
observations as rows and columns as variables, and all measurements
pertain to a single observational unit. The tidy data pattern is useful
because it allows us to see how the data relate to the design of an
experiment and the variables measured. The \texttt{dplyr} package
{[}11{]} defines an API that maps notions from the general relational
algebra to operations on tidy data. It expresses each operation as a
cohesive, endomorphic verb. Taken together these features enable a user
to write human readable analysis workflows.

@@

The \texttt{plyranges} DSL is built on the most general Bioconductor
data structure, GRanges, which is capable of representing all types of
genomic data at a semantic level that roughly matches the intuition of
most users. A GRanges is essentially a table, with columns for the
chromosome, start and end coordinates, and the strand, along with an
arbitrary set of additional columns, consisting of measurements or
metadata specific to the data type or experiment. For example, a GRanges
can represent a gene with its chromosomal coordinates, exonic structure,
and a count column summarized from an RNA-seq experiment.

By definition GRanges follows the tidy data pattern: it is a rectangular
table corresponding to a single biological context. Each row contains a
single observation and each column is a variable about that observation.
Hence, we have designed the \texttt{plyranges} DSL to extend the grammar
and design principles of \texttt{dplyr}: cohesion, consistency,
endomorphism, and fluency. All of these principles are defined and
discussed below in the context of the GRanges class. Where applicable we
contrast our design to the existing Bioconductor infrastructure.

\subsection{Genomic Relational
Algebra}\label{genomic-relational-algebra}

The \texttt{plyranges} DSL defines an expressive algebra for performing
genomic arithemtic withn and between GRanges objects. Often in analyses
of genomic regions we are required to make adjustments to the start,
end, and width columns. This is supported directly in \texttt{plyranges}
via extending the \texttt{mutate()} function in \texttt{dplyr} (table
1). However, often adjustments need to be relative: there is a mutual
dependence between the start, end and width columns over a genomic
region. Changing the start,column needs to change either the width or
the end to preserve integrity of the object. The GRanges object by
design, causes a user to think of the range as a pair of endpoints, and
hence we have developed operators that perform coordinate transfomations
with the notion of an `anchoring' combinator.

For width modification, we can stretch the range by a fixed amount or
resize the width of a range. The `anchoring' combinator preserves one of
the endpoints or the midpoint of a range when altering performing width
modification. It can also be used to preserve coordinates over strand,
for example, anchoring over the three prime end of a genomic region,
will preserve the start on the negative strand and end on the positive
strand. Anchoring the width would not make sense, because it is not a
point that can be intuitively anchored and stretching and resizing
obviously modify the width, so it would not apply to those.

Transformations that are width invariant are designed to be explicit
about the direction to modify and are performed via the shift operator.
For GRanges objects strand modulates direction and we distinguish
left/right (chromosomal coordinates) from the direction of
transcription. To generate flanking regions, we use the flank operator
which is also explicit about the direction of the input range.

Binary operations between two ranges mostly align with set operations
that treat ranges as sets of integers. These are parallel/vectorized
operations between two vectors/tables of ranges, and are not to be
confused with the aggregating operations defined in table x. We make the
binary nature of these operators by having in-fix functions in R for the
parallel union, intersect and asymetric set difference. There are also
operations that relate to the relative positions of two ranges such as
the `between' operator which returns the range in the gap between two
ranges and the `span' operator a range that spans both ranges. The
binary operations can be expressed within the functions in table x.

Our algebra recasts the actions of finding overlaps or nearest
neighbours between two genomic regions as a relational join operator.
The join operator acts on two GRanges object, a query and a subject. The
join operator is relational in the sense that metadata from the query
and subject ranges is retained in the joined range. The commonality
between all join operators in the \texttt{plyranges} DSL is to use the
index of where in the query range the subject range `hits' the query
range as a primary key (figure \ref{fig:olaps-fig}). The notion of
`hits' and hence the resulting key is determined by the type of join
(preceding, nearest, follows overlaps).

{\centering \includegraphics[width=400pt]{olaps-figure}

\caption{Illustration of the three overlap join operators. Each join takes query and subject range as input (black and grey rectangles, respectively) with associated metadata (pink and orange rectangles respectively). An index for the join is computed via returning a Hits object, which contains the indices of where the subject overlaps the query range. This index is used to expand the query or (take the intersect) of the query ranges with subject ranges and return metadata associated with each input. This principle is gnerally applied through the `plyranges` DSL for both overlaps and nearest neighbour operations.}\label{fig:olaps-fig}
\end{figure}

@@

@@

\begin{itemize}
\tightlist
\item
  compute coverage as an example here
\end{itemize}

@@

\subsection{Opportunities}\label{opportunities}

A caveat to constructing a compatible interface with \texttt{dplyr} is
that \texttt{plyranges} makes extensive use of non-standard evaluation
in R (achieved via the \texttt{rlang} package {[}14{]}). Simply, this
means that computations are performed and evaluated in the context of
the GRanges objects; emphasising the interactive nature of our API.
Consequently, when programming with \texttt{plyranges} a user needs to
be aware of how non-standard evaluation in R works and how to adapt
their code accordingly. However, with the rise of R packages like
\texttt{rlang} this process is becoming less difficult.

While GRanges are an intuitive representation for data measured on
genomic regions, more flexible data structures are required to represent
data from multiple sample experiments. The Bionconductor class
SummarizedExperiment is the canonical data structure for representing
data for combining multiomic measurements from multiple samples. The
grammar and design of the \texttt{plryanges} DSL can be naturally
extended to the SummarizedExperiment.

@@

Here we provide examples on how to use the \texttt{plyranges} DSL to
construct genomic data workflows and highlight its interoperability with
existing Bionconductor packages.

@@

The Bioconductor package \texttt{AnnotationHub} {[}15{]} can be used to
search for BigWig files from ChIP-Seq experiments from the Human
Epigenome Roadmap project {[}16{]}. Here we focus on assays for primary
T CD8+ memory cells from peripheral blood. Using \texttt{plyranges} we
will read the BigWig file corresponding to the H3 lysine 27
trimethylation (H3K27Me3) methylation mark over chromosome 10.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{chr10_scores <-}\StringTok{ }\NormalTok{bw_file }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{read_bigwig}\NormalTok{(}\DataTypeTok{overlap_ranges =}\NormalTok{ chr10_ranges) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{set_genome_info}\NormalTok{(}\DataTypeTok{genome =} \StringTok{"hg19"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\subsection{Quality Control Metrics}\label{quality-control-metrics}

We have created a GRanges object from genotyping performed on the H1
cell line, consisting of approximately two million single nucleotide
polymorphisms (SNP) and short insertion/deletions (indel). The GRanges
object consists of 7 columns, relating to the alleles of a SNP or indel,
the B-allele frequency, log relative intensity of the probes, GC content
score over a probe, and the name of the probe. We can use this
information to compute the transition-transversion ratio, a quality
control metric, within each chromosome in GRanges object.

First we filter out any insertion or deletion alleles and the SNPs
present on the mitochondria then create a logical vector corresponding
to whether there is a transition event.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{h1_snp_array <-}\StringTok{ }\NormalTok{h1_snp_array }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\NormalTok{(ref }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"I"}\NormalTok{, }\StringTok{"D"}\NormalTok{)), seqnames }\OperatorTok{!=}\StringTok{ "M"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{transition =}\NormalTok{ (ref }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"A"}\NormalTok{, }\StringTok{"G"}\NormalTok{) }\OperatorTok{&}\StringTok{ }\NormalTok{alt }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"G"}\NormalTok{,}\StringTok{"A"}\NormalTok{)) }\OperatorTok{|}
\StringTok{                      }\NormalTok{(ref }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"C"}\NormalTok{,}\StringTok{"T"}\NormalTok{) }\OperatorTok{&}\StringTok{ }\NormalTok{alt }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"T"}\NormalTok{, }\StringTok{"C"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

We can then compute the transition-transversion ratio using the
\texttt{group\_by} and \texttt{summarise} pattern, it is computed as the
total number of transition SNPs divided by the total number of
transversion SNPs within each chromsome (figure \ref{fig:titv-viz}).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ti_tv_results <-}\StringTok{ }\NormalTok{h1_snp_array }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(seqnames) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{n_snps =} \KeywordTok{n}\NormalTok{(),}
            \DataTypeTok{ti_tv =} \KeywordTok{sum}\NormalTok{(transition) }\OperatorTok{/}\StringTok{ }\KeywordTok{sum}\NormalTok{(}\OperatorTok{!}\NormalTok{transition)) }
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics{paper_files/figure-latex/titv-viz-1}

\caption{Dot plot of chromosomes ordered by estimated transition-transversion ratio. A white reference line is drawn at the expected ratio for a human exome.}\label{fig:titv-viz}
\end{figure}

@@

Another common operation in genomics data analysis is to compute data
summaries over genomic windows. In \texttt{plyranges} this can be
achieved via the \texttt{group\_by\_overlaps} operator. Continuing with
the data from the Human Epigenome Roadmap Consortium data, we can count
the number of reads that fall into a fixed bins of size 10000bp over a
BAM file of H3K27Me3 methylation marks from the H1 cell line. We extract
reads that have a mapping quality score greater than 20:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{alignments <-}\StringTok{ }\KeywordTok{read_bam}\NormalTok{(h1_bam) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(mapq }\OperatorTok{>}\StringTok{ }\DecValTok{20}\NormalTok{) }
\end{Highlighting}
\end{Shaded}

Note that the BAM file is only read into memory once we perform an
operation on it. Next we generate our genomic bins using the
\texttt{tile} function from \texttt{GenomicRanges}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{bins <-}\StringTok{ }\KeywordTok{tile}\NormalTok{(h1_bam, }\DataTypeTok{width =} \DecValTok{10000}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Finally, we can use \texttt{group\_by\_overlaps} with \texttt{summarise}
to compute the total number of reads within each window.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{h1_bam_read_summary <-}\StringTok{ }\NormalTok{h1_bam }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{group_by_overlaps}\NormalTok{(bins) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{n_reads =} \KeywordTok{n}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

https://support.bioconductor.org/p/71601/ also useful example?

@@

The \texttt{plyranges} package is available on the Bioconductor project
website \url{https://bioconductor.org} or can be accessed via Github
\url{https://github.com/sa-lee/plyranges}. We aim to continue developing
the \texttt{plyranges} package and extend it for use with more complex
data structures such as the SummarizedExperiment class, which can be
used for analysing transcriptomic and variant data. As the
\texttt{plyranges} interface encourages tidy data practices it
integrates well with the principles of the grammar of graphics, we aim
to use it to prepare data for the visualisation of multimodal biological
datasets.

\section{Acknowledgements}\label{acknowledgements}

We would like to thank Dr Matthew Ritchie at the Walter and Eliza Hall
Institute and Dr Paul Harrison for their feedback on earlier drafts of
this work. We would also like to thank Lori Shepherd and Hèrve Pages for
the code review they performed. This report was written with
\texttt{knitr} {[}17{]} and the figures were made with \texttt{ggbio}
{[}18{]}. All code required to reproduce this report is available at
https://github.com/sa-lee/plyranges-paper.

@@

\hypertarget{ref-R-knitr}{}
17. Xie Y. Dynamic documents with R and knitr {[}Internet{]}. 2nd ed.
Boca Raton, Florida: Chapman; Hall/CRC; 2015. Available:
\url{https://yihui.name/knitr/}

\hypertarget{ref-R-ggbio}{}
18. Yin T, Cook D, Lawrence M. Ggbio: An r package for extending the
grammar of graphics for genomic data. Genome Biology. BioMed Central
Ltd; 2012;13: R77.
